### 2015-01-16 fundamentals/examples.tex
more language to tie things in

The \Cyclus community-driven software development model seeks to break the unproductive cycle proliferating overspecialized simulators and 
to leverage the collective expertise of fuel cycle researchers. Through the 
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@

Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
have been 
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being 
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, storage
facilities, and expanded institutional paradigms.  These contributed archetypes
illustrate the power of a community-based development approach.

@@

>>>>

The \Cyclus community-driven software development model seeks to break the 
unproductive proliferation of overspecialized simulators and instead leverages 
the collective expertise of fuel cycle researchers toward a single, more 
extensible, tool. Through the targeted
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@

It is expected that the most common type of contribution to \Cyclus will be 
contributions of new archetypes. Researchers will be driven to create a new 
archetype when a need arises to represent a novel reactor type, an innovative 
reprocessing strategy, or a particular governmental or institutional behavior.  
The real-world utility of \Cyclus can in part be measured by the breadth and 
diversity of archetypes being developed in this way.

Early progress has been promising. Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
have been 
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being 
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, storage
facilities, and expanded institutional paradigms.

@@

The existence and diversity of these contributed archetypes
illustrate the power and potential of the community-based development approach 
that \Cyclus has taken.
